The unphysicality of Hilbert spaces

### 2024-09-03 Articles/2023-HilbertQuantum/Submissions/Quantum Studies/HilbertQuantum.tex
Incorporated Francisco's comments

Unitary transformations play an important role in the theory of Hilbert spaces for at least two reasons. The first is that two Hilbert spaces that differ by a unitary transformation are mathematically equivalent. For example, changes of basis and changes of variables are unitary transformations. This is already a problem: the space of wave-functions for $n$ particles is the Hilbert space $L^2(\mathbb{R}^{3n})$. For any value of $n$, these spaces have a countable basis (i.e. infinite dimensional and separable) and are therefore all mathematically equivalent. That is, the state space for one particle is the same as the state space for, say, a billion particles. We can therefore theoretically construct a quantum channel that encodes the information of a billion particles into a single one. Note that this is not possible in classical mechanics: the state space for $n$ classical particles is $\mathbb{R}^{6n}$. For different $n$, these spaces are not even topologically equivalent.

@@

Additionally, Schwartz spaces would be physical only if we are modeling a fixed number of degrees of freedom over Euclidean space. We would still need a more general definition that would apply to all cases and would reduce to Schwartz spaces in the above case.

>>>>

Unitary transformations play an important role in the theory of Hilbert spaces for at least two reasons. The first is that two Hilbert spaces that differ by a unitary transformation are mathematically equivalent. For example, changes of basis and changes of variables are unitary transformations. This is already a problem: the space of wave-functions for $n$ particles is the Hilbert space $L^2(\mathbb{R}^{3n})$. For any value of $n$, these infinite-dimensional spaces are separable, meaning that they all have a countable basis, and so are unitarily equivalent. That is, the state space for one particle is the same as the state space for, say, a billion particles. We can therefore theoretically construct a quantum channel that encodes the information of a billion particles into a single one. Note that this is not possible in classical mechanics: the state space for $n$ classical particles is $\mathbb{R}^{6n}$. For different $n$, these spaces are not even topologically equivalent.

@@

Additionally, Schwartz spaces can only represent physical systems with a fixed number of degrees of freedom over Euclidean space. It is not clear how to generalize the definition to cover all physical cases.
